Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2017-07-11 paper.tex
Add description of noscat and scat formulations

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figure-mfps-50km}
  \caption{Mean free paths
    representative of the collapse profile at
    50~km ($\varrho=10^{11}\,{\rm g}\,{\rm cm}^{-3}$,
    $T=3.7$~MeV, $Y_e=0.12$).
    In the fluid rest frame these are given by
    $(\chi^*_a)^{-1}$ for the absorption
    and $(\chi_s)^{-1}$ for elastic scattering interactions.
  }
  \label{fig:mfps-50km}
\end{figure}

>>>>

In the following we present two forms of the integrated distribution functions,
Eqns.~\ref{eqn:num_fae} and \ref{eqn:num_fse}:
1) the full form  by which the solution is $f_{\rm scat}=f_{\rm AE}+f_{\rm SE}$
(labeled `scat' since we include elastic scattering), and
2) the form treating only absorption/emission interactions
in which we set $\mathscr{K}_{\rm SE}=0$ so that $f_{\rm noscat}=f_{\rm AE}$
(labeled `no scat' since we ignore elastic scattering).
There is no simple relation between the two forms for a given ray; that is
$f_{\rm scat} \neq f_{\rm noscat}+f_{\rm SE}$.
This is because $f_{\rm AE}$ is integrated using solely the absorption optical
depth in the first form,
and the absorption plus scattering optical depth in the second form.
Before this work, the noscat form of the equations has been the standard for
ray tracing, though many authors include the scattering optical depth in
the integration of Eqn.~\ref{eqn:num_fae}
(see for example \cite{hari2010-gr_nunubar_collapsar}).
\todo{explain why; cite others}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figure-mfps-50km}
  \caption{Mean free paths
    representative of the collapse profile at
    50~km ($\varrho=10^{11}\,{\rm g}\,{\rm cm}^{-3}$,
    $T=3.7$~MeV, $Y_e=0.12$).
    In the fluid rest frame these are given by
    $(\chi^*_a)^{-1}$ for the absorption
    and $(\chi_s)^{-1}$ for elastic scattering interactions.
    Computed using \lstinline{NuLib}, as in the ray tracing code.
  }
  \label{fig:mfps-50km}
\end{figure}
